---
author: Your Name
date: '`r format(Sys.Date())`'
title: Homework Assignment
---
## Exercises 

We are going to use the __HistData__ package. If it is not installed you can install it like this:

```{r, eval=FALSE}
install.packages("HistData")
```

Load the height data set and create a vector `x` with just the male heights used in Galton's data on the heights of parents and their children from his historic research on heredity.

```{r, eval=FALSE}
library(HistData)
data(Galton)
x <- Galton$child
```

1\. Compute the average and median of these data.

2\. Compute the median and median absolute deviation of these data.



3\. Now suppose Galton made a mistake when entering the first value and forgot to use the decimal point. You can imitate this error by typing:

```{r, eval=FALSE}
x_with_error <- x
x_with_error[1] <- x_with_error[1]*10
```

How many inches does the average grow after this mistake?

4\. How many inches does the SD grow after this mistake?

5\. How many inches does the median grow after this mistake?

6\. How many inches does the MAD grow after this mistake?

7\. How could you use exploratory data analysis to detect that an error was made?

a. Since it is only one value out of many, we will not be able to detect this.
b. We would see an obvious shift in the distribution.
c. A boxplot, histogram, or qq-plot would reveal a clear outlier.
d. A scatterplot would show high levels of measurement error.


8\. How much can the average accidentally grow with mistakes like this? Write a function called `error_avg` that takes a value `k` and returns the average of the vector `x` after the first entry changed to `k`. Show the results for `k=10000` and `k=-10000`.

## Case study: self-reported student heights 
